Object-Oriented Internet - Azure Interoperability

### 2020-12-02 Latex/Manuscript.tex
Final review of the latex text #37
- Review PS proposals - unimportant modification

This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. The proposals are backed by proof of concept reference implementations. Prototyping addresses Microsoft Azure Cloud as an example. The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) [TODO: Add reference?]. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.

@@

Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler. It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up. At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services. The transfer process requires data conversion from source to destination encoding. The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication [TODO: Reference]. This communication is transparent, i.e.~it is not data types aware allowing
any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT and HTTPS.

>>>>

This article addresses further research on the integration of the CPS in the context of new emerging disciplines, i.e.~Industry 4.0 (I4.0) and the Internet of Things (IoT). The new architecture is proposed for integration of the multi-vendor \textbf{machine-centric} CPS designed atop of M2M reactive communication and emerging cloud computing as a \textbf{human-centric} front-end. To support the multi-vendor environment OPC Unified Architecture \cite{LiteratureSurveyOnOpenPlatformCommunications} interoperability standard has been selected. The proposals are backed by proof of concept reference implementations. Prototyping addresses Microsoft Azure Cloud as an example. The prototyping outcome has been just published on GitHub as the open-source (MIT licensed) \todo{Add reference}. The proposed solutions have been harmonized with the more general concept called the Object-Oriented Internet.

@@

Following the assumption that interconnection between the CPS and cloud services is designed based on the gateway concept, a middleware must be considered as a coupler. It must be interconnected with the CPS using an in-band protocol adhering to communications requirements (i.e.~protocol profile, data encoding, time relationships, etc.) governing communication of the parts making it up. At the same time, it must support back-and-forth data transfer to the cloud using out-of-band native for the cloud services. The transfer process requires data conversion from source to destination encoding. The \textit{IoT\ Hub} is a service hosted in the cloud that supports \textit{IoT\ Central} providing a robust messaging solution - it acts as a central message hub for bi-directional communication \todo{Reference}. This communication is transparent, i.e.~it is not data types aware allowing
any devices to exchange any kind of data. This service is responsible to manage the devices' identity and it offers the following protocol stacks: AMQP, MQTT and HTTPS.
